A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-09-19 journal/introduction.tex
start response, edits

Chen et al. defined the \emph{fuzzer taming problem}: ``Given a potentially large collection of test cases, each of which triggers a bug, rank them in such a way that test cases triggering distinct bugs are early in the list.'' \cite{PLDI13}.  Their proposed solution was to use the Furthest-Point-First \cite{Gonzalez} (FPF) algorithm.  An FPF ranking of test cases requires a distance metric $d$ on test cases, and ranks test cases so that dissimilar tests appear earlier.  The hypothesis of Chen et al. was that dissimilar tests, by a well-chosen metric, will also fail due to different faults.
FPF is a greedy algorithm that proceeds by repeatedly adding the item with the maximum minimum distance to all previously ranked items. Given an initial seed item $r_0$, a set
$S$ of items to rank, and a distance metric $d$, FPF computes $r_i$ as $s \in S: \forall s' \in S: min_{ j < i}(d(s,r_j)) \geq min_{j < i}(d(s',r_j))$.

@@

This not a claim that being repaired by the same mutant perfectly predicts fault equivalence.  To understand why that seems highly unlikely, consider why a mutant of a compiler might cause a test case to stop failing.  Many, likely most, compiler faults are due to incorrect optimizations.  Turning an optimization off can cause a program to compile correctly.  Optimizations are generally guarded by conditional switches --- in some cases, so that the optimization can be turned off by a user, in other cases when a property of the code in question prevents the optimization.  If two failures become successes due to turning off an optimization, it is presumably \emph{some} level of evidence they are the same fault, compared to the baseline probability.  Intuitively, the evidence provided seems much stronger than the fact that, e.g., the two test cases execute a shared line of code \cite{RepsSpectra}.  However, optimization guards range from guarding very specific fragments of code to guarding entire modules with many functions and related sub-optimizations.  If a mutant prevents a very specific optimization (consisting of a few lines of code) from executing, and repairs two tests, that is powerful evidence they are related.  If a mutant turns off a large number of optimizations, it is weak evidence.  Must we then characterize mutant granularity?  No.

>>>>

Chen et al. defined the \emph{fuzzer taming problem}: ``Given a potentially large collection of test cases, each of which triggers a bug, rank them in such a way that test cases triggering distinct bugs are early in the list.'' \cite{PLDI13}.  Their proposed solution was to use the Furthest-Point-First \cite{Gonzalez} (FPF) algorithm.  An FPF ranking of test cases requires a distance metric $d$ on test cases, and ranks test cases so that dissimilar tests appear earlier.  The hypothesis of Chen et al. was that dissimilar tests, by a well-chosen metric, will also fail due to different faults.
FPF is a greedy algorithm that proceeds by repeatedly adding the item with the maximum minimum distance to all previously ranked items. Given an initial seed item $r_0$, a set
$S$ of items to rank, and a distance metric $d$, FPF computes $r_i$ as $s \in S: \forall s' \in S: min_{ j < i}(d(s,r_j)) \geq min_{j < i}(d(s',r_j))$.  The condition on $s$ is obviously true when $s = s'$, or when $s' = r_j$ for some $j < i$; the other cases for $s'$, however, force selection of some (possibly non-unique) max-min-distance $s$.

@@

This is not a claim that being repaired by the same mutant perfectly predicts fault equivalence.  To understand why that seems highly unlikely, consider why a mutant of a compiler might cause a test case to stop failing.  Many, likely most, compiler faults are due to incorrect optimizations.  Turning an optimization off can cause a program to compile correctly.  Optimizations are generally guarded by conditional switches --- in some cases, so that the optimization can be turned off by a user, in other cases when a property of the code in question prevents the optimization.  If two failures become successes due to turning off an optimization, it is presumably \emph{some} level of evidence they are the same fault, compared to the baseline probability.  Intuitively, the evidence provided seems much stronger than the fact that, e.g., the two test cases execute a shared line of code \cite{RepsSpectra}.  However, optimization guards range from guarding very specific fragments of code to guarding entire modules with many functions and related sub-optimizations.  If a mutant prevents a very specific optimization (consisting of a few lines of code) from executing, and repairs two tests, that is powerful evidence they are related.  If a mutant turns off a large number of optimizations, it is weak evidence.  Must we then characterize mutant granularity?  No.

### 2019-09-19 journal/localizations.tex
more small fixes
start response, edits

\begin{quote}
For a set $F$ of failing test cases and $m$ of mutants, 
the {\bf Repair} localization for $f \in F$, where $R(f) \in m$ is the set
of mutants repairing $f$, ranks
statements by the function $r$:
%$$dmax(m,f) = max_{t : m \in R(t)} d(t,f)$$
\[
r(f) = 
\begin{cases}
\frac{1}{1 + max_{t \in F: m \in R(t)} d(t,f)} & m \in R(f)\\
0 & m \not\in R(f)\\
\end{cases}
\]
%$$\text{leastfar} = m \in R(f) : \neg\exists m' : \text{far}(m',f) <
%\text{far}(m,f)$$
\end{quote}

This ranks a mutant $m$ (and associated statement) by the inverse of the distance
from $f$ to the most distant failing test also repaired by $m$, adding 1
so that if $m$ only repairs failures at distance 0 $r$ is well defined
(and maximal).
If $m$ does not repair $f$, it is not ranked at all.  One advantage of
this approach over some statistical methods is that by
ranking \emph{mutants} the localization offers developers not simply a
ranked statement but a kind of ``explanation'' \cite{GroceError} of the fault:  if \emph{this
mutant} were applied, the fault would not exhibit.  As Kochhar et
al. show \cite{Kochhar}, a large majority (more than 85\%) of developers considered
the ability of a localization tool to provide a \emph{rationale} or
reason for a localization important.  A mutation plus the tests that
stop failing when it is applied is a practical, concrete explanation
of a fault localization.  Mutants that repair a failure provide insight 
into the nature of the fault, and, we hypothesize, more information the 
closer they are to the center of the onion-ring.

@@

Another advantage over many statistical approaches to 
localization is that our methods are not potentially confused in 
settings with multiple faults.  Each localization/explanation is based 
on a single failing test case, which in most cases fails due to only one 
fault.  In fact, other faults help both methods rank localizations.

>>>>

\begin{quote}
For a set $F$ of failing test cases and $M$ of mutants, 
the {\bf Repair} localization for $f \in F$, where $R(f) \subseteq M$ is the set
of mutants repairing $f$, ranks
statements by the function $r_f(m)$:
%$$dmax(m,f) = max_{t : m \in R(t)} d(t,f)$$
\[
r_f(m) = 
\begin{cases}
\frac{1}{1 + max_{t \in F: m \in R(t)} d(t,f)} & m \in R(f)\\
0 & m \not\in R(f)\\
\end{cases}
\]
%$$\text{leastfar} = m \in R(f) : \neg\exists m' : \text{far}(m',f) <
%\text{far}(m,f)$$
\end{quote}

This ranks a mutant $m$ (and associated statement) by the inverse of the distance
from $f$ to the most distant failing test also repaired by $m$, adding 1
so that if $m$ only repairs failures at distance 0 $r_f$ is well defined
(and maximal).
If $m$ does not repair $f$, it is not ranked at all.  One advantage of
this approach over some statistical methods is that by
ranking \emph{mutants} the localization offers developers not simply a
ranked statement but a kind of ``explanation'' \cite{GroceError} of the fault:  if \emph{this
mutant} were applied, the fault would not exhibit.  As Kochhar et
al. show \cite{Kochhar}, a large majority (more than 85\%) of developers considered
the ability of a localization tool to provide a \emph{rationale} or
reason for a localization important.  A mutation plus the tests that
stop failing when it is applied is a practical, concrete explanation
of a fault localization.  Mutants that repair a failure provide insight 
into the nature of the fault, and, we hypothesize, more information the 
closer they are to the center of the onion-ring.

@@

### 2019-09-19 journal/metrics.tex
start response, edits

This metric, the portion of mismatches over bits that are 1 in either
vector, matches our intuitions about the above comparisons.  It
essentially formalizes the intuition of the onion-ring model, where
more matching repairs indicates a much higher probability two failures
are due to the same fault, even if not all repairs match.

>>>>

\noindent In other words, the Jaccard distance is $\frac{\mathit{bitcount}(u
\veebar v)}{\mathit{bitcount}(u \vee v)}$ (the number of 1 bits in the
XOR over the number of 1 bits in the OR for $u$ and $v$); that is, the
distance is the portion of mismatches over repairing mutants for
either test.  This metric agrees with our intuitions about the above comparisons.  It
essentially formalizes the intuition of the onion-ring model, where
more matching repairs indicates a much higher probability two failures
are due to the same fault, even if not all repairs match.
